Learning by Teaching a Robot:\\The Case of Handwriting

### 2015-12-27 main.tex
Remove extraneous info re eigenvalues

By changing the eigenvalues associated to these eigenvectors and regenerating
letters with the reverse procedure, it becomes then easy to generate new
letters, with distortions that are actually plausible handwriting errors: they
are exaggerations of variance of writing styles that naturally occurs amongst
adult writers.  Figure~\ref{fig:sampleLetters} shows examples of deformed ``g''
generated with such a technique.

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{cowriter-g}
    \caption{\small \label{fig:sampleLetters} \textbf{Generating bad letters}:
        effect of varying the first five eigenvalues (rows) of the shape model
        of ``g'' by different factors (columns). The percentage of the total
        variance in the dataset explained by each eigenvalue is shown      on
        the appropriate row. Examples noted A, B, C, D illustrate how the
        PCA-based approach allows to \emph{automatically} generate letters whose
        errors can be \emph{semantically} interpreted, \eg A has a too large bottom
        loop, B has a wide top loop, the bottom loop of C is not correctly
        closed, the top loop of D is not closed, etc.}

@@

The same technique can also be applied to \emph{classify} demonstrations,
\emph{assess} their quality and \emph{learn} from them. Figure~\ref{fig:h} shows
for example nine allographs of ``h'' written by a 6 years old child, along with
the mean letter from the dataset (reference letter). By projecting each of the
demonstrations onto the eigenspace of ``h'' (Figure~\ref{fig:h}b), we observe
that:

>>>>

New letters can be generated by varying the weightings in linear combinations of
these eigenvectors, with distortions that are actually plausible handwriting errors: 
they are exaggerations of variations of writing styles that naturally occur amongst
adult writers.  Figure~\ref{fig:sampleLetters} shows examples of deformed ``g''
generated with such a technique.

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{cowriter-g}
    \caption{\small \label{fig:sampleLetters} \textbf{Generating bad letters}:
        effect of independently varying the weightings (columns) of the first five eigenvectors 
        (rows) of the shape model of ``g''. Examples A, B, C, D illustrate how the
        PCA-based approach allows for the \emph{automatic} generation of letters whose
        errors can be \emph{semantically} interpreted, \eg A has too large a bottom
        loop, B has a wide top loop, the bottom loop of C is not correctly
        closed, the top loop of D is not closed, etc.}

@@

The same shape model can also be used to \emph{classify} demonstrations,
\emph{assess} their quality and \emph{learn} from them. Figure~\ref{fig:h} shows
for example nine allographs of ``h'' written by a 6 years old child, along with
a reference letter. By projecting each of the
demonstrations onto the eigenspace of ``h'' (Figure~\ref{fig:h}b), we observe
that:
